---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Survey Solutions Paradata Viewer Application

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

<div align="justify">
The Survey Solutions Paradata Viewer Application[^1] is part of a comprehensive toolkit designed to enhance the process of survey implementation through [Survey Solutions](https://docs.mysurvey.solutions/). The underlying application allows you to visualize Survey Solutions paradata, at the questionnaire, the interviewer and the geographic level.

#### Key Features

1. **Visualization at the questionnaire level**: Review a questionnaire's average time profile, average timings and number of invalid questions.

2. **Visualization at the interviewer level**: Review average completion times, average pace and number of response removals at the level of the interviewer

3. **Visualization at the geographic level**: Review average completion times, average pace and number of response removals by geographic regions[^2]. Visualization is either through a [*mapdeck*](https://cran.r-project.org/web/packages/mapdeck/vignettes/mapdeck.html) (requires an API key) or a [*leaflet*](https://rstudio.github.io/leaflet/) map.

4. **Admin Interface**: This intuitive interface lets you:
    * Directly connect to your Survey Solutions server to load the paradata.
    * Specify the time interval when new data should be downloaded.
    
5. **Flexibility in data input**: Data can be provided as:
    * File upload.
    * Directly from the server through the API.
    * From a local directory.
    
6. **Download the data**: The application also allows to dowload the data in a more convenient format and by event type.

7. **Direct review of interviews/interviewers**: Allows you to directly connect to the Survey Solutions server and review interviews and interviewers.

8. **Report creation**: Generates a full paradata report as a word document at the:

    * *Questionnaire* level,
    * *Interviewer* level,
    * *Map* level[^3].
    


## Installation

 1. Install R: https://cran.r-project.org/mirrors.html (version 4.1.1 or greater)

 2. Install R Studio: https://rstudio.com/products/rstudio/download/ (version 1.2.5001-3 or newer)

 3. Make sure the *devtools* package is installed, if not install it with:

```{r devtoolsinst,eval=FALSE, echo=TRUE}
install.packages("devtools")

```


 4. After that install the actual package:

```{r install,eval=FALSE, echo=TRUE}
devtools::install_github("michael-cw/susoparaviewer")

```

## Running the application interactively

You can either run the application interactively: 

```{r start, eval=FALSE, echo=TRUE}
library(susoparaviewer)
susoparaviewer::runParaApp()

```


## Running the application on a Shiny Server

...or run the application on your own shiny server. In this case, create a directory, i.e. susoparaviewer and put a file called *app.R* with the following code into it:

```{r start_srv, eval=FALSE, echo=TRUE}
library(susoparaviewer)
susoparaviewer::runParaAppServer()

```


#### Attention - Potential issue with 'shinyalert'

There's a known issue with the 'shinyalert' package from Dean Attali, which may cause the application to fail during start-up on certain Windows installations running the latest version of R. For more details, please check this [issue](https://github.com/daattali/shinyalert/issues/75).

This issue has been resolved in the development version of 'shinyalert', but the fix is not yet available in the official CRAN release. If you encounter this problem, please install the development version for 'shinyalert' using the following command:


```{r install_alert,eval=FALSE, echo=TRUE}
devtools::install_github("daattali/shinyalert")

```

## Feature requests and bug reports

You can either use the standard GitHub approach by filing a bug report/feature request [here](https://github.com/michael-cw/SurveySolutionsAPI/issues) or you use the Survey Solutions user forum [here](https://forum.mysurvey.solutions/c/api/13).

Please continue to check for updates, as we are constantly working to improve the application.


[^1]: Funding was received from the [Joint Development Data Center on Forced Displacement](https://www.jointdatacenter.org/) .

[^2]: Only available if geographic coordinates had been collected.

[^3]: Only available if geographic coordinates had been collected.
</div>
